---
title: "ECON 700 Main Page"
author: "Bob McNab"
date: "`r Sys.Date()`"
output: 
  html_document:
    self_contained: true
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: true
      right: true
    fig_width: 5
    fig_height: 5
    dev: jpeg
knit: >
  (function(inputFile, ...) {
    rmarkdown::render(inputFile, output_file = 'index.html')
  })
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Test 

I am testing ECON 700. This is a simple test.

For more details, see econ 700.

Testing again

Trying to figure this out.

```{r}

x <- 5
y <- 10
print(x*y)

```



When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
